Formal verification of train route planning

### 2025-06-27 paper/main.tex
typos

\begin{wrapfigure}[10]{r}{0.28\textwidth}
	\begin{minipage}{0.28\textwidth}
		\centering
		\vspace{-8mm}
		\includegraphics[height=30mm]{maquette.png}
		\caption{The model.}
		\label{fig:maquette}
	\end{minipage}
\end{wrapfigure}

@@

\paragraph{Experiments}  With TLA+, we checked that any safe step is actually (not surprisingly!) reliable.  On our network, one finds 58 368 safe steps, all being reliable. Checking all the paths took XXX seconds on YYY. %\todo{XXX= nombre de seconde, YYY = décrire la machine (processeur, RAM, etc)}

@@

Our third contribution is a composition operator. This operator allows to incrementally build routing schedules, which can then be tested using our TLA+ implementation. Our composition distinguishes safe steps: steps where no two trains use the same track. Our composition can append safe steps to arbitrary schedules, creating new schedules. We implemented our composition operator in Python and we tested it by model checking all schedules composed of two and three safe steps in our small-scale network. The computation time was found to be affordable for companies: checking all two-steps schedules took less than a day on a cluster, using 8 nodes of 18 cores.

>>>>

\begin{wrapfigure}[10]{r}{0.28\textwidth}
	\begin{minipage}{0.28\textwidth}
		\centering
		\vspace{-0mm}
		\includegraphics[height=30mm]{maquette.png}
		\caption{The model.}
		\label{fig:maquette}
	\end{minipage}
\end{wrapfigure}

@@

\paragraph{Experiments}  With TLA+, we checked that the 58 368 safe step are actually (not surprisingly!) correct. Checking all the paths took XXX seconds on YYY. %\todo{XXX= nombre de seconde, YYY = décrire la machine (processeur, RAM, etc)}

@@

Our third contribution is a composition operator. This operator allows to incrementally build routing schedules, which can then be tested using our TLA+ implementation. Our composition distinguishes safe steps: steps where no two trains use the same track. Our composition can append safe steps to arbitrary schedules, creating new schedules. We implemented our composition operator in Python and we tested it by model checking all schedules composed of two and three safe steps in our small-scale network. The computation time was found to be affordable for companies: checking all two-steps schedules took less than an hour on a cluster, using 8 nodes of 18 cores.
